X\texorpdfstring{\textsuperscript{2}}-Toon: An Extended X-Toon Shader

### 2013-04-15 paper/paper.tex
Added new images and descriptions to paper Added new section to future work

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/inverse_lighting}
	\caption{Inverse Lighting result}
	\label{fig:inverseLighting}
\end{figure*}

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/lighting}
	\caption{Lighting result}
	\label{fig:lightingResult}
\end{figure*}

\begin{figure}[h]
	\centering
	\includegraphics[width=1.5in]{images/xtoon_shading_gradient}
	\caption{Tone texture for lighting}
	\label{fig:gradient}
\end{figure}

@@

@@

>>>>

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/inverse_lighting}
	\caption{Inverse Lighting result. The model appears to be lit from the opposite direction but no lighting variables or directions have been altered.}
	\label{fig:inverseLighting}
\end{figure*}

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/lighting}
	\caption{Lighting result. The model appears to self-shadow itself using only the tone detail texture.}
	\label{fig:lightingResult}
\end{figure*}

\begin{figure}[h]
	\centering
	\includegraphics[width=1.5in]{images/xtoon_shading_gradient}
	\caption{Tone texture for lighting. This gives the effect of self-shadowing on a model, especially when combined with lighting directions.}
	\label{fig:gradient}
\end{figure}

@@

\begin{figure*}[h]
 \centering
 \includegraphics[width=5.5in]{images/dissolve}
 \caption{A dissolving effect. Using the lighting directions and the generated tone detail texture we were able to give the impression of the model dissolving in and out of view.}
 \label{fig:dissolve}
\end{figure*}

\begin{figure*}[h]
 \centering
 \includegraphics[width=5.5in]{images/metallic}
 \caption{A metallic sheen effect. The light directions give the model a metallic look as the tone detail texture reacts to new directions.}
 \label{fig:metallic}
\end{figure*}

@@

\subsection{Animated tone detail texture}
We also discussed the possibility of using an animated tone detail texture in lieu of a static image. This could create many new effects such as hologram noise and colour shifting without the need to change tone detail or shading values. Futures works should investigate the use of an animated tone detail texture and devise new effects that can be generated with this method.
